---
title: "Data Science for Supply Chain"
output:
  pdf_document: default
  html_notebook: default
---

### Moving Average 
The average demand during the last n periods. 
$$
f_n = \frac{1}{n}\sum_{i=1}^n{d_{t-i}}
$$

Where:

* $n$ is the number of periods we take the average of 
* $d_t$ the demand we observe during period $t$ 
* $f_t$ is the forecast we made for period $t$ 

The first
forecast will be done for $t=n+1$ 

In scientific literature, you will find often see the output you want to predict noted $y$

A prediction would be noted as $\hat{y}$

When we want to point to a specific occurrence of the forcast at time $t$, we will not it $f_t$ or $d_t$ 

Demand observation: we will call the demand of each period. 


**Noise**: an unexplained variation in the data. It is often due to the randomness of the different processes at hand. 


## References 
* [Moving Average: ](http://uc-r.github.io/ts_moving_averages)

```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(fpp2)
library(zoo)
```

```{r}

dmd <- tibble::tribble(
              ~Date, ~Demand,
         "2010-1-1",      37,
         "2011-1-1",      60,
         "2012-1-1",      85,
         "2013-1-1",     112,
         "2014-1-1",     132,
         "2015-1-1",     145,
         "2016-1-1",     179,
         "2017-1-1",     198,
         "2018-1-1",     212,
         "2019-1-1",     232,
         "2020-1-1",      NA,
         "2021-1-1",      NA,
         "2022-1-1",      NA
         )



dmd$Date <- as.Date(dmd$Date)

demand <- dmd %>% mutate(srate_ma_1 = rollmean(Demand, k = 4, fill = NA, align = "right"),
                         srate_ma_2 = rollmean(Demand, k = 5, fill = NA, align = "right"), 
                          srate_ma_3 = rollmean(Demand, k = 6, fill = NA, align = "right")) 

demand

demand %>% gather(metric, value, Demand:srate_ma_3) %>% 
  ggplot(aes(Date, value, color = metric)) + 
  geom_line()
```

